---
title: "CPTAC.BRCA.Tutorial.Phospho"
author: "Efstathios Vlachavas"
date: "2022-09-29"
output: html_document
editor_options: 
  chunk_output_type: console
---

Firstly, load the necessary R packages

```{r}

library(tidyverse)
library(limma)
library(decoupleR)
library(readr)
library(OmnipathR)
library(org.Hs.eg.db)
library(ggplot2)
library(forcats)
library(statmod)
library(limma)
library(vsn)
library(hexbin)

```

Start with the phosphoproteomics analysis

```{r}
# load your phospho-proteome data
# if they are raw intensities: filter out phosphosites with many NAs (> 20%), perform VSN normalization
# remove duplicates combinations of Gene+Phosphosite (will lead to problems with duplicated rownames later on)

pak1_phospho = read.delim("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_151933_20240826_Exp61_PAK1inh_PHOSPHO_Report_loc95.txt")

pak1_phospho$gene_site = sapply(strsplit(pak1_phospho$T..PTM_collapse_key, split = "_", fixed = T), function(x) paste0(x[1], "_", x[2]))

# remove NaN
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))

pak1_phospho[is.nan.data.frame(pak1_phospho)] <- NA


table(duplicated(pak1_phospho$gene_site))
# sum up duplicated sites:
duplicated_sites = unique(pak1_phospho$gene_site[duplicated(pak1_phospho$gene_site)])
length(duplicated_sites)


replace_duplicates_with_sum = function(data){
  for (i in 1:length(duplicated_sites)){
    data[data$gene_site == duplicated_sites[i],1:19] <- rep(apply(data[data$gene_site == duplicated_sites[i],1:19],2,sum,na.rm=T), each = nrow(data[data$gene_site == duplicated_sites[i],]))
    
  }
  return(data)
}

pak1_phospho_duplicated_summed = pak1_phospho

pak1_phospho_duplicated_summed = replace_duplicates_with_sum(pak1_phospho_duplicated_summed)

nrow(pak1_phospho_duplicated_summed)

pak1_phospho_duplicated_summed=pak1_phospho_duplicated_summed[!duplicated(pak1_phospho_duplicated_summed$gene_site),]
nrow(pak1_phospho_duplicated_summed)
#22,064 out of 25,233

pak1_phospho_duplicated_summed[pak1_phospho_duplicated_summed==0]<-NA



# QC:
par(mar=c(10,5,5,5))
barplot(apply(pak1_phospho_duplicated_summed[,1:19], 2, function(x) sum(!is.na(x))), las = 2)

boxplot(log2(pak1_phospho_duplicated_summed[,1:19]), las = 2)


# remove MCF7 standard
pak1_phospho_duplicated_summed = pak1_phospho_duplicated_summed[,-7]

# normalize
library(limma)
pak1_phospho_duplicated_summed_norm = pak1_phospho_duplicated_summed[,1:18]
rownames(pak1_phospho_duplicated_summed_norm) = pak1_phospho_duplicated_summed$gene_site

pak1_phospho_duplicated_summed_norm = limma::normalizeVSN((pak1_phospho_duplicated_summed_norm))

boxplot(pak1_phospho_duplicated_summed_norm, las = 2)

library(pheatmap)
column_annotation = data.frame(cell_line = rep(c("LTED", "TAMR", "WT"), each = 6), treatment = rep(c("DMSO", "inh", "DMSO", "inh", "DMSO", "inh"), c(3,3,3,3,3,3)), replicate = rep(1:3, 6))
rownames(column_annotation) = colnames(pak1_phospho_duplicated_summed_norm)

pheatmap(na.omit(pak1_phospho_duplicated_summed_norm), scale = "row", annotation_col = column_annotation, color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100), breaks = seq(-3,3,6/100))

write.csv(pak1_phospho_duplicated_summed_norm, file = "K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/Pak1_inh_PHOSPHO_duplSummed_VSNnorm.csv")

########################################################################################
# START HERE WITH NORMALIZED, FILTERED, DUPLICATES SUMMED DATA
##########################################################################################
#
#
#



norm.mat_duplicated_summed = read.csv("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/Pak1_inh_PHOSPHO_duplSummed_VSNnorm.csv", header = T, stringsAsFactors = F, row.names = 1)
#


#metadata:
cell_line = sapply(strsplit(colnames(norm.mat_duplicated_summed), split = "_", fixed = T), function(x) x[1])
treatment =  sapply(strsplit(colnames(norm.mat_duplicated_summed), split = "_", fixed = T), function(x) x[2])

my_sample_col <- data.frame(cell_line =cell_line, treatment = treatment)
row.names(my_sample_col) <- colnames(norm.mat_duplicated_summed)


# continue with setting the design matrix and perform DE analysis with limma R package
# create a vector that contains the different conditions of your experiment (in the order that they appear in your data --> best use the colnames (minus replicates))

cond_vec = as.factor(paste0(cell_line, "_",treatment))
table(cond_vec)
# Then we continue with first step of the construction of the OMNIPATH network

# import KSN from omnipath
omnipath_ptm <- get_signed_ptms()

# likely erroneous database records: As all databases, the resources constituting OmniPath contain wrong records, some of them more, others less. Here we see all these records are from only one resource called ProtMapper. ProtMapper uses literature mining algorithms (REACH, Sparser), which are known to produce a number of false positives in their output. On this premise:

omnipath_ptm <- omnipath_ptm %>% filter(!grepl('ProtMapper', sources) | n_resources > 1)

# Which means: not from ProtMapper, or from more than one resource (i.e. if it is from ProtMapper, but also another resource confirms, then we keep the record).

omnipath_ptm <- omnipath_ptm[omnipath_ptm$modification %in% c("dephosphorylation","phosphorylation"),]
KSN <- omnipath_ptm[,c(4,3)]
KSN$substrate_genesymbol <- paste(KSN$substrate_genesymbol,omnipath_ptm$residue_type, sep ="_")
KSN$substrate_genesymbol <- paste(KSN$substrate_genesymbol,omnipath_ptm$residue_offset, sep = "")
KSN$mor <- ifelse(omnipath_ptm$modification == "phosphorylation", 1, -1)
KSN$likelihood <- 1

#we remove ambiguous modes of regulations
KSN$id <- paste(KSN$substrate_genesymbol,KSN$enzyme_genesymbol,sep ="")
KSN <- KSN[!duplicated(KSN$id),]
KSN <- KSN[,-5]

#rename KSN to fit decoupler format for downstream analysis
names(KSN)[c(1,2)] <- c("phospho_site","kinase")

# Implement a specific plotting function:
# https://github.com/saezlab/kinase_tf_mini_tuto/blob/main/code/utils.R
 
plot_top_features <- function(data, n_top) {

  colnames(data) <- "value"

  arranged <- data %>%
    as.data.frame() %>%
    tibble::rownames_to_column(var = "id") %>%
    arrange(desc(value))

  top_up <- slice_head(arranged, n = n_top)
  top_down <- slice_tail(arranged, n = n_top)

  p <- bind_rows(list(up = top_up, down = top_down), .id = "status") %>%
    mutate(id = fct_inorder(id)) %>%
    ggplot(aes(x = value, y = id, fill = status)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("up" = "red4", "down" = "mediumblue")) +
    theme_bw()

  return(p)

}

#design <- model.matrix(~0 + cond_vec) #unpaired design for responderDMSO vs. nonresponder DMSO comparison

design <- model.matrix(~0 + cond_vec)
colnames(design) <- gsub("cond_vec", "", colnames(design))

colnames(design)


phospho.mat = norm.mat_duplicated_summed
nrow(design)
ncol(phospho.mat)
head(phospho.mat)

######################################################################
######################################################################

library(limma)
#filter for at least 3/4 values per condition:
condition1 = "WT_inh"
condition2 = "WT_DMSO"

condition1_columns = (1:ncol(phospho.mat))[cond_vec == condition1]
colnames(phospho.mat)[condition1_columns]
condition2_columns = (1:ncol(phospho.mat))[cond_vec == condition2]
colnames(phospho.mat)[condition2_columns]

# only include sites with 3/3 values
phospho.mat.condition = phospho.mat[apply(phospho.mat[,condition1_columns], 1, function(x) sum(!is.na(x))) > 2 & apply(phospho.mat[,condition2_columns], 1, function(x) sum(!is.na(x))) > 2,]
nrow(phospho.mat)
nrow(phospho.mat.condition)

head(phospho.mat.condition)

fit <- lmFit(phospho.mat.condition,design)

#change the comparison that you want 
##!!! rename


contrast_name <- paste0(condition1, '-', condition2)
contrast_name

cm <- limma::makeContrasts(contrasts=eval(contrast_name),
                                        levels=design)


fit2 <- contrasts.fit(fit, cm)

fit3 <- eBayes(fit2, trend=T,robust = T)

#
comp1_stat <- limma::topTable(fit3, coef=1, number=nrow(fit3), adjust.method="fdr", sort.by="none") 





# the comp1_stat data frame needs to consist of a single column containing the T-stats
# the rownames have to be gene_phosphosite (e.g. AKT1_S473)
head(comp1_stat)

# this we will use downstream for pathway activity
comp1_stat_downstream <- limma::topTable(fit3, coef=1, number=nrow(fit3), adjust.method="fdr", sort.by="none") %>% 
  dplyr::select(t) %>% 
  dplyr::rename(!!contrast_name :=t) %>% 
  drop_na() %>%
  rownames_to_column() %>% 
  separate("rowname", sep="_", into=c("GeneSymbol","PhosID"))

head(comp1_stat_downstream)
# matrix should contain GeneSymbol, PhosID and Stats

setwd("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/")
write.csv(comp1_stat, file = paste0("20240827_PHOSPHO_",contrast_name,"_stats.csv"), row.names = T)

comp1_stat = read.csv("20240827_PHOSPHO_LTED_inh-LTED_DMSO_stats.csv", row.names = 1)

# refine the network to include kinases with at least 5 targets
KSN_exp_1 <- intersect_regulons(as.matrix(comp1_stat), KSN, .source = kinase, .target = phospho_site, minsize=5) 


kin_activity_1 <- run_wmean(mat = as.matrix(comp1_stat), .source = "kinase", .target = "phospho_site",network = KSN_exp_1, times = 1000)

#format the DF for visualization purposes
kin_activity_1 <- kin_activity_1[kin_activity_1$statistic == "norm_wmean",c(2,4)] %>% column_to_rownames(var="source")

# also save the total output to investigate in more detail
kin.activity.output <- kin_activity_1 %>% rownames_to_column(var="Omnipath_Kinase")
head(kin.activity.output)

write_tsv(kin.activity.output,file=paste0("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_kinase_activities_",contrast_name,".tsv"))



# Separate EDA plots wih the top10 UO/DOWN MOST PERTURBED KINASES FOR THE 3 COMPARISONS
plot_top_features(kin_activity_1, n_top = 20) +
  ggtitle(contrast_name)





# merge results:
WT_kinases = read.delim("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_kinase_activities_WT_inh-WT_DMSO.tsv")
LTED_kinases = read.delim("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_kinase_activities_LTED_inh-LTED_DMSO.tsv")
TAMR_kinases = read.delim("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_kinase_activities_TAMR_inh-TAMR_DMSO.tsv")

kinases_merged = merge(WT_kinases, LTED_kinases, by = "Omnipath_Kinase", all = T)
kinases_merged = merge(kinases_merged, TAMR_kinases, by = "Omnipath_Kinase", all = T)
colnames(kinases_merged)[2:4] = c("WT", "LTED", "TAMR")
rownames(kinases_merged) = kinases_merged$Omnipath_Kinase
kinases_merged = kinases_merged[,-1]

pheatmap(kinases_merged, scale = "none", cluster_rows = F, cluster_cols = F, color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100), breaks = seq(-2,2,4/100))

plot(kinases_merged$LTED, kinases_merged$TAMR, pch = 16, col = "#00000080", xlab = "LTED PAK1-inh vs. DMSO", ylab = "TAMR PAK1-inh vs. DMSO", main = "kinase activity changes upon PAK1-inhibition", cex = 1)
abline(h=2, lty = 2, col = "#ea513f")
abline(v=2, lty = 2, col = "#ea513f")
abline(h=-2, lty = 2, col = "#5390c1")
abline(v=-2, lty = 2, col = "#5390c1")

library(wordcloud)
kinases_merged = kinases_merged[!is.na(kinases_merged$LTED) & !is.na(kinases_merged$TAMR),]
text_to_plot = na.omit(rownames(kinases_merged)[abs(kinases_merged$LTED) > 2 | abs(kinases_merged$TAMR) > 2])
x_coord = na.omit(kinases_merged$LTED[abs(kinases_merged$LTED) > 2 | abs(kinases_merged$TAMR) > 2])
y_coord = na.omit(kinases_merged$TAMR[abs(kinases_merged$LTED) > 2 | abs(kinases_merged$TAMR) > 2])

textplot(x_coord, y_coord, text_to_plot, new = F, show.lines = T)


# plot intensity of PAK1 target sites
PAK1_targets = KSN$phospho_site[KSN$kinase == "PAK1"]
PAK1_targets_identified = PAK1_targets[PAK1_targets %in% rownames(phospho.mat)]
#39
pheatmap(na.omit(phospho.mat[PAK1_targets_identified,]), scale = "row", cluster_rows = T, cluster_cols = F, color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100), breaks = seq(-2,2,4/100))

# stats:

WT_stats = read.csv("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_PHOSPHO_WT_inh-WT_DMSO_stats.csv", header = T, stringsAsFactors = F, row.names = 1)

LTED_stats = read.csv("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_PHOSPHO_LTED_inh-LTED_DMSO_stats.csv", header = T, stringsAsFactors = F, row.names = 1)
TAMR_stats = read.csv("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/20240827_PHOSPHO_TAMR_inh-TAMR_DMSO_stats.csv", header = T, stringsAsFactors = F, row.names = 1)


# VOLCANO
# #########################################
plot(TAMR_stats$logFC, -log10(TAMR_stats$adj.P.Val), pch = 16, col = "#00000050", xlim = c(-4,4))
#add known target sites:
points(pak1.stats.merged$TAMR_logFC, -log10(pak1.stats.merged$TAMR_adj.P.Val),pch=16, col = "red")
#add predicted target sites:
points(TAMR_stats$logFC[rownames(TAMR_stats) %in% paste0(nature_pak1_sites$Gene, "_", nature_pak1_sites$Phosphosite)], -log10(TAMR_stats$adj.P.Val)[rownames(TAMR_stats) %in% paste0(nature_pak1_sites$Gene, "_", nature_pak1_sites$Phosphosite)],pch=16, col = "blue")

textplot(data.matrix(TAMR_stats$logFC)[abs(TAMR_stats$logFC) > 2 | TAMR_stats$adj.P.Val < 0.01], data.matrix(-log10(TAMR_stats$adj.P.Val))[abs(TAMR_stats$logFC) > 2 | TAMR_stats$adj.P.Val < 0.01], rownames(TAMR_stats)[abs(TAMR_stats$logFC) > 2 | TAMR_stats$adj.P.Val < 0.01], new = F)


# potential new PAK1 target sites:
# nature paper about target landscape of Ser/Thr kinases
setwd("K:/Ergebnisse/LS_testing/1_PhD/paper/EGF_dynamics/additional_plots/kinase_assignment/")
nature_paper_result = read.csv("nature_paper_result.csv", header = T, stringsAsFactors = F, sep = ",")

nature_pak1_sites = nature_paper_result[nature_paper_result$PAK1_percentile>98 & nature_paper_result$PAK1_rank <6,]
# 288 potential pak1 target sites
nature_pak1_sites$gene_site = paste0(nature_pak1_sites$Gene, "_", nature_pak1_sites$Phosphosite)

nature_pak1_identified = nature_pak1_sites$gene_site[nature_pak1_sites$gene_site %in% rownames(phospho.mat)]
######################
PAK1_targets_identified = union(PAK1_targets_identified, nature_pak1_identified)

WT_stats.pak1 = na.omit(WT_stats[PAK1_targets_identified,])
barplot(WT_stats.pak1$logFC[order(WT_stats.pak1$logFC, decreasing = T)], las = 2, names.arg = rownames(WT_stats.pak1)[order(WT_stats.pak1$logFC, decreasing = T)])

LTED_stats.pak1 = na.omit(LTED_stats[PAK1_targets_identified,])

barplot(LTED_stats.pak1$logFC[order(LTED_stats.pak1$logFC, decreasing = T)], las = 2, names.arg = rownames(LTED_stats.pak1)[order(LTED_stats.pak1$logFC, decreasing = T)], main = "LTED: T-stats of PAK1 target sites upon PAK1-inhibition")


TAMR_stats.pak1 = na.omit(TAMR_stats[PAK1_targets_identified,])
barplot(TAMR_stats.pak1$logFC[order(TAMR_stats.pak1$logFC, decreasing = T)], las = 2, names.arg = rownames(TAMR_stats.pak1)[order(TAMR_stats.pak1$logFC, decreasing = T)], main = "TAMR: T-stats of PAK1 target sites upon PAK1-inhibition")


pak1.stats.merged = merge(WT_stats.pak1, LTED_stats.pak1, by = 0, all = T)
rownames(pak1.stats.merged) = pak1.stats.merged$Row.names
pak1.stats.merged = pak1.stats.merged[,-1]
pak1.stats.merged = merge(pak1.stats.merged, TAMR_stats.pak1, by = 0, all = T)
rownames(pak1.stats.merged) = pak1.stats.merged$Row.names
pak1.stats.merged = pak1.stats.merged[,-1]

colnames(pak1.stats.merged) = paste0(rep(c("WT", "LTED", "TAMR"), each = 6),"_",colnames(pak1.stats.merged))
pak1.stats.merged$gen = sapply(strsplit(rownames(pak1.stats.merged), "_"), function(x) x[1])

table(pak1.stats.merged$gen)

par(mar=c(10,5,5,5))
barplot(t(data.matrix(pak1.stats.merged[,c(7,13)])), beside = T, las = 2, legend.text = T)
barplot(t(data.matrix(-log10(pak1.stats.merged[,c(10,16)]))), beside = T, las = 2, legend.text = T)


# scatter plot:
phospho.mat = read.csv("K:/Ergebnisse/LS_testing/1_PhD/01_experiments/Exp61_MCF7_LTED_TAMR_WT_PAK1-inh_treatment_phosphoMS/Pak1_inh_PHOSPHO_duplSummed_VSNnorm.csv", row.names = 1)

phospho.mat.pak1 = phospho.mat[rownames(phospho.mat) %in% PAK1_targets_identified,]
phospho.mat.pak1$source = rep("omnipath", nrow(phospho.mat.pak1))
phospho.mat.pak1$source[rownames(phospho.mat.pak1) %in% nature_pak1_identified] <- "predicted"

colnames(phospho.mat.pak1)

phospho.mat.pak1$LTED_FC = apply(phospho.mat.pak1[,1:6], 1, function(x) mean(x[4:6]-x[1:3], na.rm=T))

phospho.mat.pak1$LTED_sd = apply(phospho.mat.pak1[,1:6], 1, function(x) sd(x[4:6]-x[1:3], na.rm=T))

phospho.mat.pak1$TAMR_FC = apply(phospho.mat.pak1[,7:12], 1, function(x) mean(x[4:6]-x[1:3], na.rm=T))

phospho.mat.pak1$TAMR_sd = apply(phospho.mat.pak1[,7:12], 1, function(x) sd(x[4:6]-x[1:3], na.rm=T))

phospho.mat.pak1= phospho.mat.pak1[!is.na(phospho.mat.pak1$LTED_FC) & !is.na(phospho.mat.pak1$TAMR_FC),]

phospho.mat.pak1$LTED_p = rep(NA, nrow(phospho.mat.pak1))
phospho.mat.pak1$TAMR_p = rep(NA, nrow(phospho.mat.pak1))

phospho.mat.pak1$LTED_p[apply(phospho.mat.pak1[,1:6],1,function(x) sum(!is.na(x))) == 6] = apply(phospho.mat.pak1[apply(phospho.mat.pak1[,1:6],1,function(x) sum(!is.na(x))) == 6,1:6], 1, function(x) t.test(x[1:3],x[4:6])$p.value)


phospho.mat.pak1$TAMR_p[apply(phospho.mat.pak1[,7:12],1,function(x) sum(!is.na(x))) == 6] = apply(phospho.mat.pak1[apply(phospho.mat.pak1[,7:12],1,function(x) sum(!is.na(x))) == 6,1:6], 1, function(x) t.test(x[1:3],x[4:6])$p.value)


plot(data.matrix(phospho.mat.pak1$LTED_FC), data.matrix(phospho.mat.pak1$TAMR_FC), pch = 16, xlab = "log2 FC PAK1-inh vs DMSO (LTED)", ylab = "log2 FC PAK1-inh vs DMSO (TAMR)",
     main = "changes in PAK1 substrates phosphorylation", xlim = c(-2,2), ylim = c(-2,2), col = as.factor(phospho.mat.pak1$source))

abline(h=0, lty = 2)
abline(v=0, lty = 2)
library(wordcloud)



interesting.lted = phospho.mat.pak1[abs(phospho.mat.pak1$LTED_FC) > 1 |abs(phospho.mat.pak1$TAMR_FC) > 1 ,]
interesting.lted = interesting.lted[!is.na(interesting.lted$LTED_FC),]

textplot(interesting.lted$LTED_FC, interesting.lted$TAMR_FC, rownames(interesting.lted),new = F, show.lines = T)
















FC_colors = data.frame(color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100),FC = seq(-2,2,4/99))
border_color = rep("lightgrey", nrow(TAMR_stats.pak1))
border_color[TAMR_stats.pak1$adj.P.Val < 0.05] <- "red"


par(mar=c(10,5,5,5))
barplot(TAMR_stats.pak1$logFC[order(TAMR_stats.pak1$logFC, decreasing = T)], las = 2, names.arg = rownames(TAMR_stats.pak1)[order(TAMR_stats.pak1$logFC, decreasing = T)], main = "TAMR: T-stats of PAK1 target sites upon PAK1-inhibition", col = FC_colors$color[sapply(TAMR_stats.pak1$logFC[order(TAMR_stats.pak1$logFC, decreasing = T)], function(x) sum(x > FC_colors$FC))], border = border_color[order(TAMR_stats.pak1$logFC, decreasing = T)])


# LTED:
FC_colors = data.frame(color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100),FC = seq(-2,2,4/99))
border_color = rep("lightgrey", nrow(LTED_stats.pak1))
border_color[LTED_stats.pak1$adj.P.Val < 0.05] <- "red"


par(mar=c(10,5,5,5))
barplot(LTED_stats.pak1$logFC[order(LTED_stats.pak1$logFC, decreasing = T)], las = 2, names.arg = rownames(LTED_stats.pak1)[order(LTED_stats.pak1$logFC, decreasing = T)], main = "LTED: T-stats of PAK1 target sites upon PAK1-inhibition", col = FC_colors$color[sapply(LTED_stats.pak1$logFC[order(LTED_stats.pak1$logFC, decreasing = T)], function(x) sum(x > FC_colors$FC))], border = border_color[order(LTED_stats.pak1$logFC, decreasing = T)])



pak1_merged = merge(LTED_stats.pak1, TAMR_stats.pak1, by = 0, all = T)
rownames(pak1_merged) = pak1_merged$Row.names
colnames(pak1_merged)[2:7] = paste0("LTED_", colnames(pak1_merged)[2:7])
colnames(pak1_merged)[8:13] = paste0("TAMR_", colnames(pak1_merged)[8:13])

pheatmap(pak1_merged[,c(2,8)], scale = "none", cluster_rows = F, cluster_cols = F, color = colorRampPalette(c("#5390c1", "white", "#ea513f"))(100), breaks = seq(-2,2,4/100))
```


```{r}
plot(pak1_merged$LTED_logFC.x, pak1_merged$TAMR_logFC.y, pch = 16, col = "#00000080", xlab = "LTED PAK1-inh vs. DMSO", ylab = "TAMR PAK1-inh vs. DMSO", main = "log2FC of PAK1 target sites", cex = 1)
abline(h=0, lty = 2)
abline(v=0, lty = 2)


library(wordcloud)

text_to_plot =rownames(pak1_merged)[!is.na(pak1_merged$LTED_logFC.x) & !is.na(pak1_merged$TAMR_logFC.y)]
x_coord = pak1_merged$LTED_logFC.x[!is.na(pak1_merged$LTED_logFC.x) & !is.na(pak1_merged$TAMR_logFC.y) ]
y_coord = pak1_merged$TAMR_logFC.y[!is.na(pak1_merged$LTED_logFC.x) & !is.na(pak1_merged$TAMR_logFC.y) ]

textplot(x_coord, y_coord, text_to_plot, new = F, show.lines = T)

points(pak1_merged$LTED_logFC.x, pak1_merged$TAMR_logFC.y, pch = 16, col = "#876cad", cex =abs(pak1_merged$LTED_t.x)/3)
points(pak1_merged$LTED_logFC.x, pak1_merged$TAMR_logFC.y, pch = 16, col = "#d76d17", cex =abs(pak1_merged$TAMR_t.y)/3)

legend("topright", bty = "n", pch = 16, cex = c(1/2, 5/2, 10/2), col = "#876cad", legend = c("1", "5", "10"))

